A Poll-of-Polls Forecast for the 2024 U.S. Presidential Election: Kamala Harris Emerges as a Leading Candidate with Constant Support Rates Hovering Around 50%

### 2024-10-29 paper/paper.qmd
results graph updates

The original dataset sourced from FiveThirtyEight [@fivethirtyeight2024] aggregates a wide range of poll results (16264 observations, based on dataset available at Oct 24, 13:00). The polls conducted by various polling organizations capture voter preferences by taking a representative sample of the electorate and asking for the voters' candidate of choice. Surveys were conducted at the state and national levels, providing the wide perspective on public feelings across the country.

@@

Our results are summarized in @tbl-modelresults1 and @tbl-modelresults2.
[!!! ADD MORE WORDS !!!]

@@

## Stability in Support Levels for Harris {#sec-first-point}

@@

## Pollster-Specific Variability {#sec-second-point}

>>>>

The original dataset sourced from FiveThirtyEight [@fivethirtyeight2024] aggregates a wide range of poll results (16506 observations, based on dataset available at Oct 29). The polls conducted by various polling organizations capture voter preferences by taking a representative sample of the electorate and asking for the voters' candidate of choice. Surveys were conducted at the state and national levels, providing the wide perspective on public feelings across the country.

@@

## Results from the relation between the prediction variable and outcome variable of the analysis data

@fig-resultplot1 shows an initial increase in support following Harris' announcement, peaking around mid-September. However, this initial momentum stabilized with minor decrease in support as the election gets closer. Moreover, the scattered data points around the summary line show high variance between individual polls.

```{r}
#| label: fig-resultplot1
#| fig-cap: "Polling votes for Harris over time *Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024."
#| echo: false
base_plot <- ggplot(harris_data, aes(x = end_date, y = pct)) +
  theme_classic() +
  labs(y = "Harris percent", x = "Date")

# Plots poll estimates and overall smoothing
base_plot +
  geom_point() +
  geom_smooth()
```

When @fig-resultplot2

```{r}
#| label: fig-resultplot2
#| fig-cap: "Polling votes for Harris over time by pollster *Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024. Only filtered pollsters with high-quality polling questions are shown in the following."
#| echo: false
# Color by pollster
base_plot +
  geom_point(aes(color = pollster)) +
  geom_smooth() + 
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-resultplot3
#| fig-cap: "Polling votes for Harris over time by pollster (facets) *Note:* The date starts from after Harris officially announced her campaign for 2024 U.S. presidential election on July 21, 2024. Only filtered pollsters with high-quality polling questions are shown in the following."
#| echo: false
# Facet by pollster
base_plot +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x)) +  # Use GAM smoothing to handle complex data
  facet_wrap(vars(pollster))
```

## Results from the prediction model

Prediction results derived from our model frameworks are summarized in @tbl-modelresults1 and @tbl-modelresults2.
[!!! ADD MORE WORDS !!!]

@@

## Why Harris could beat her polls {#sec-first-point}

@@

## Pollsters herding around false consensus {#sec-second-point}

The polling averages for Harris and Trump don't seem to show a big difference.
